Compositional Certified Resource Bounds

### 2014-07-03 paper/main.tex
add cool figure
minor changes

\begin{figure*}
\centering
\begin{tabular}{c|c|c|c}
%
\begin{lstlisting}
while (z > y)
  y++;
while (y > 2)
  y -= 3;
\end{lstlisting}
&
\begin{lstlisting}
while (i > 100)
  i--;
i += k+50;
while (i >= 0)
  i--;
\end{lstlisting}
&
\begin{lstlisting}
while (x > 0) {
  x--;
  t=x, x=y, y=t;
}
\end{lstlisting}
&
\begin{lstlisting}
assert(y >= 0);
while (x>y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    /* skip */;
}
\end{lstlisting}
\\
%
\hline
t08 (slightly modified) & t19 & t30 & t15
%
\end{tabular}
\caption{
  Comparison of the bounds given by different tools on
  linear examples.
}
\label{fig:compar}
\end{figure*}

@@

In the development of our quantitative Hoare logic we have drawn
inspiration from mechanically verified Hoare logics.
Nipkow's~\cite{Nipkow02} description of his implementations of Hoare
logics in Isabelle/HOL has been helpful to understand the interaction
of auxiliary variables with the consequence rule.  The consequence
rule we use in our Coq implementation is a quantitative version of a
consequence rule that has been attributed to Martin Hofmann by
Nipkow~\cite{Nipkow02}.  Appel's separation logic for CompCert
Clight~\cite{AppelLogic} has been a blueprint for the general
structure of the quantitative logic.  Since we do not deal with memory
safety, our logic is much simpler and it would be possible to
integrate it with Appel's logic.  The continuation passing style that
we use in the quantitative logic is not only used by
Appel~\cite{AppelLogic} but also in Hoare logics for low-level
code~\cite{NiS06,JensenBK13}.

>>>>

\begin{figure*}
\centering
\begin{tabular}{c|c|c|c}
%
\begin{lstlisting}
while (y > x) {
  x++; tick(1) }
while (x > 2) {
  x -= 3; tick(1) }
\end{lstlisting}
&
\begin{lstlisting}
while (i > 100)
  i--;
i += k+50;
while (i >= 0)
  i--;
\end{lstlisting}
&
\begin{lstlisting}
while (x > 0) {
  x--;
  t=x, x=y, y=t;
}
\end{lstlisting}
&
\begin{lstlisting}
assert(y >= 0);
while (x>y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    /* skip */;
}
\end{lstlisting}
\\
%
\hline
t08a (slightly modified t08) & t19 & t30 & t15
%
\end{tabular}
\caption{
  Comparison of the bounds given by different tools on
  linear examples.
}
\label{fig:compar}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for example
  \emph{t8a}. For $x\ge 0$ the derived bound is tight.}
\label{fig:3d}
\end{figure}

@@

In the development of our quantitative Hoare logic we have drawn
inspiration from mechanically verified Hoare logics.
Nipkow's~\cite{Nipkow02} description of his implementations of Hoare
logics in Isabelle/HOL has been helpful to understand the interaction
of auxiliary variables with the consequence rule.  Appel's separation
logic for CompCert Clight~\cite{AppelLogic} has been a blueprint for
the general structure of the quantitative logic.  Since we do not deal
with memory safety, our logic is much simpler and it would be possible
to integrate it with Appel's logic.  The continuation passing style
that we use in the quantitative logic is not only used by
Appel~\cite{AppelLogic} but also in Hoare logics for low-level
code~\cite{NiS06,JensenBK13}.
